Type Refinements for the Working Class

### 2015-11-12 paper.tex
Revamp the ambient logical framework in terms of presheaves

\newcommand\Hom[3]{#1\left[#2,#3\right]}

@@

\todo[inline]{explain general and hypothetical judgment with respect to ABTs (probably
following Bob's book).}

>>>>

\newcommand\Hom[3]{#1\!\left[#2,#3\right]}

@@

For any abt signature $\Match{\Sigma}{\Pair{\Sorts}{\Operators}}$ and a worlds
category $\mathcal{W}$, we may deploy a general logical framework in which the
meaning of a judgment is an object of the presheaf category
$\Define{\mathbb{J}}{\Sets^\mathcal{W}}$ (that is, a judgment is identified
with the intensional set of its derivations).

\begin{definition}[General Judgment]
  For a metavariable context $\IsMetaCtx{\Omega}$, we can define the set
  of its substitutions as the following product:
  \[
    \Define{[\Omega]}{
      \prod_{\MV{m}:v} \MkSet{E\mid\IsAbtUnmoded{\cdot}{\cdot}{\cdot}{E}{v}}
    }
  \]
  Let $\Discrete{[\Omega]}$ be the discrete category on $[\Omega]$. Then, for
  any diagram $\Of{\mathcal{J}}{\mathbb{J}^{\Discrete{[\Omega]}}}$, we can
  define the general judgment $\GenJ{\Omega}{\mathcal{J}}$ as follows:
  \[
    \textstyle
    \Define{
      \left(\GenJ{\Omega}{\mathcal{J}}\right)(w)
    }{
      \Hom{\mathbb{J}}{
        \Yoneda{w}
      }{
        \varinjlim_{\Discrete{[\Omega]}}\mathcal{J}
      }
    }\qquad
    (\Member{w}{\mathcal{W}})
  \]

  Intuitively, the general judgment $\GenJ{\Omega}{\mathcal{J}}$ is evident
  when the family of judgments $\mathcal{J}$ shall forevermore have a section
  (i.e. for any substitution of $\Member{\omega}{[\Omega]}$,
  $\mathcal{J}(\omega)$ shall be evident). Recall that metavariables have
  \emph{valences} rather than sorts; as such, the general judgment allows us to
  quantify over terms of higher type.  However, for clarity we will often write
  $\GenJ{\MV{m}:\sigma}{\mathcal{J}}$ rather than
  $\GenJ{\MV{m}:\MkValence{\cdot}{\cdot}{\sigma}}{\mathcal{J}}$; likewise, in
  the body of $\mathcal{J}$ we will simply write $\MV{m}$ rather than the more
  proper $\MApp{\MV{m}}{\cdot}{\cdot}$.

\end{definition}

\begin{definition}[Hypothetical Judgment]

  For two judgments $\mathcal{J}_1$ and $\mathcal{J}_2$, we can form the
  hypothetical judgment $\HypJ{\mathcal{J}_2}{\mathcal{J}_1}$, which expresses
  the semantic consequence of $\mathcal{J}_2$ from $\mathcal{J}_1$:
  \begin{align*}
    \ADefine{
      \left(\HypJ{\mathcal{J}_2}{\mathcal{J}_1}\right)(w)
    }{
      \left({\mathcal{J}_2}^{\mathcal{J}_1}\right)(w)
    }\\
    &\cong
    \OMode{
      \Hom{\mathbb{J}}{
        \Yoneda{w}\times\mathcal{J}_1
      }{
        \mathcal{J}_2
      }
    }
  \end{align*}

  Intuitively, the hypothetical judgment
  $\Define{\HypJ{\mathcal{J}_2}{\mathcal{J}_1}}{\mathcal{J}_1\to\mathcal{J}_2}$
  is evident when there shall forevermore be an effective transformation of the
  evidence into the evidence of the consequent. It is important to keep in mind
  that this is a \emph{semantic} consequence and therefore expresses
  admissibilities, in contrast to the the \emph{logical} consequence which
  expresses derivabilities \cite{harper:2016}. We will not have any need for
  the latter.
\end{definition}
